
# Package dependencies
- zip : to generate the zip files that contain the programs or the results to submit to the Codalab platform.

```{r label = "Submission - dependencies", include = FALSE}
if ( !exists(x = "params") ) {
    params                      <- NULL
}
if ( is.null(x = params$package_repository) ) {
    params$package_repository   <- "https://cloud.r-project.org"
}
if ( is.null(x = params$install_dependencies) ) {
    params$install_dependencies <- TRUE
}
print(params)
if ( params$install_dependencies ) {
    installed_packages <- installed.packages( )
    for (package in c("zip") ) {
        if ( !{ package %in% installed_packages } ) {
            print(x = paste("Installation of ", package, sep = "") )
            install.packages(
                pkgs = package
              , repos = params$package_repository
            )
        } else {
            print(x = paste(package, " is installed.", sep = "") )
        }
    }
    remove(list = c("installed_packages", "package") )
}
```

# Format of the submission

- **For a code submission** : you have to make a zip file (no constrain on the namefile) that contains :
  - the file `metadata` that is generated by this script
  - your code inside a *R* file named `program.R`. This file will be sourced and have to contain :
  - a function `program` with `data_train` and `data_test` as argument : a matrix associated to your prediction.
  - any other files that you want to access from your function `program` : during the ingestion phase (when your code is evaluated), the working directory will be inside the directory obtained by unzipping your submission.
  
- **For a result submission** : you have to make a zip file (no constrain on the namefile), with your results as a matrix inside a rds file named `results.txt`.


# Configuration of your result

```{r label = "Submission - configuration", echo = TRUE, results = "verbatim"}
    ##
    ## EDIT THE FOLLOWING CODE BY COMMENTING/UNCOMMENTING THE REQUIRED PARTS
    ##
    
    ## define the public data set that you will use for your prediction :
    data_train <- readRDS(file = "data_train.rds")
    data_test <- readRDS(file = "data_test.rds")
```

# Write a function to predict test set train set

In the provided example, we use a naive method to generate the baseline prediction.

```{r label = "Submission - Program", echo = TRUE, results = "verbatim"}
#' The function use a naive method to generate the baseline prediction.
#'
#' @param data_train a matrix
#' @param data_test a matrix
#' @return the estimated parameters
#' @examples
#' program(data_train = data_train, data_test = data_test)
program <- function(data_train, data_test) {
    genes = colnames(data_test)[-(1:3)]

    ##
    ## YOUR CODE BEGINS HERE
    ## 
    
    # use the first gene as predictor for sex
    g = genes[1]
    plot(data_train$sex, data_train[,g])
    formula = as.formula(paste0("sex~", g))
    print(formula)
    m = glm(formula, data_train, family =binomial(link = 'logit'))
    pred = predict.glm(m, data_test, type="response")
    data_pred = ifelse(pred<0.5, levels(data_train$sex)[1], levels(data_train$sex)[2])


    # # use SIS model (Zhang HH. J R Stat Soc Series B Stat Methodol. 2008) with lowest p-value
    # ms = sapply(genes, function(g){
    #   print(g)
    #   formula = as.formula(paste0("sex~", g))
    #   m = glm(formula, data_train, family=binomial(link = 'logit'))
    #   pval = summary(m)$coefficients[2,4]
    #   beta = m$coefficients[[2]]
    #   return(c(pval=pval, beta=beta))
    # })
    # plot(ms["beta",], -log10(ms["pval",]))
    # g = colnames(ms[,order(ms["pval",])])[1]
    # formula = as.formula(paste0("sex~", g))
    # print(formula)
    # m = glm(formula, data_train, family =binomial(link = 'logit'))
    # pred = predict.glm(m, data_test, type="response")
    # data_pred = ifelse(pred<0.5, levels(data_train$sex)[1], levels(data_train$sex)[2])

    
    ##
    ## YOUR CODE ENDS HERE
    ##

    return(data_pred)
    
}
```

# Generate a prediction

```{r label = "Submission - Results", echo = TRUE, results = "verbatim"}
    ##
    ## DO NOT CHANGE THE FOLLOWING CODE
    ##

    ## we use the previously defined function 'program' to estimate A :
    data_pred <- program(
      data_train = data_train,
      data_test = data_test
    )
```

# Generate a zip file with the 'program' source code

```{r label = "Submission - program zip file", echo = TRUE, results = "verbatim"}
if ( !dir.exists(paths = "submissions") ) {
    dir.create(path = "submissions")
}

## we save the source code as a R file named 'program.R' :
dump(
    list = c("program")
  , file = paste0("submissions", .Platform$file.sep, "program.R")
)
## we also generate the 'metadata' file
cat(
    "command: Rscript $program/program.R $input $output"
  , file = paste0("submissions", .Platform$file.sep, "metadata")
)

## we create the associated zip file :
zip_program <- paste0("submissions", .Platform$file.sep, "program_", format(x = Sys.time( ), format = "%Y_%m_%d_%S"), ".zip")
zip::zipr(
         zipfile = zip_program
       , files   = paste0("submissions", .Platform$file.sep, c("program.R", "metadata") )
     )
print(x = zip_program)
```

# Generate a zip file with the prediction

```{r label = "Submission - results zip file", echo = TRUE, results = "verbatim"}
if ( !dir.exists(paths = "submissions") ) {
    dir.create(path = "submissions")
}

## we save the estimated A matrix as a rds file named 'results.txt' :
# saveRDS(
#     object = data_pred
#   , file   = paste0("submissions", .Platform$file.sep, "results.rds")
# )

write.table(
  x=data_pred, 
  file= paste0("submissions", .Platform$file.sep, "results.txt"),
  quote=FALSE,
  row.names=FALSE,
  col.names=FALSE
)


## we create the associated zip file :
zip_results <- paste0("submissions", .Platform$file.sep, "results_", format(x = Sys.time( ), format = "%Y_%m_%d_%S"), ".zip")
zip::zipr(
         zipfile = zip_results
       , files   = paste0("submissions", .Platform$file.sep, c("results.txt") )
     )
print(x = zip_results)
```

# Submit the zip file

It generates the files *`r zip_program`*  and *`r zip_results`*  (the 1st one for code submission, the 2nd one for result submission).

Submit the zip submission file on the challenge in the tab `Participate`, menu `Submit / View Results` menu, sub-menu `CHALLENGE #1`, by clicking the `Submit` button after filling out some metadatas.

On the codalab challenge web page, The *STATUS* become : 
  - Submitting
  - Submitted	
  - Running
  - Finished

When it’s finished :
  - You refresh the page and see your score
  - If enable, details for report could be downloaded by clicking *Download output from scoring step*.
  - Some logs are available to download.
  - Leader board is updated in the `Results` tab.

# Session Information

```{r, results="verbatim"}
sessionInfo( )
```
